This section illustrates a use case of TinyML in controlling an unmanned ground 
vehicle (UGV). A video demonstration of the experiment described below is 
linked in the \href{https://github.com/gadepall/aiml#TinyML}{README} of the 
repository.

\subsection{Components}
\begin{table}[!ht]
    \centering
    \input{tiny-ml/ugv/tables/ugv-components.tex}
    \caption{Components Required for Controlling the UGV Using TinyML.}
    \label{tab:ugv-components}
\end{table}

\subsection{Training Data}
\begin{enumerate}
    \item Download the Sensor Logger app from Google Play Store.
    \item In the settings on the app, set the sampling frequency to maximum, 
    and turn off logging uncalibrated data. Record from the device orientation 
    sensor only.
    \item Press \texttt{Start Recording}, and perform the gestures 100 times
    to gather the data.
    \item Press \texttt{Stop Recording} when you are done and export the 
    recordings as a zip file.
    \item Unzip and rename the CSV files appropriately in
    \begin{lstlisting}
tiny-ml/ugv/data
    \end{lstlisting}
    \item In the same directory, run the following commands:
    \begin{lstlisting}
gcc -O2 format.c
./a.out
    \end{lstlisting}
    \item Two more CSV files \texttt{train.csv} and \texttt{test.csv} will be 
    created in the same directory.
\end{enumerate}

\subsection{Model}
\begin{enumerate}
    \item Run the Python script
    \begin{lstlisting}
tiny-ml/ugv/codes/multi_class.py
    \end{lstlisting}
    \item Tweak the neural network parameters in this file if the accuracy is
    not satisfactory.
    \item The neural network model will be present as a bytestream in
    \begin{lstlisting}
tiny-ml/ugv/codes/client/src/gesture_model.h  
    \end{lstlisting}
\end{enumerate}

\subsection{Implementation}
\begin{enumerate}
    \item Find the IP address of your phone by using the \texttt{ifconfig}
    command.
    \item In the Sensor Logger app, set the HTTP Push URL to
    \begin{lstlisting}
http://<IP>:5000/ugv
    \end{lstlisting}
    in the app settings. Enable the HTTP Push feature.
    \item Run the server with the following commands.
    \begin{lstlisting}
cd tiny-ml/ugv/codes/server
flask run --host <IP>
    \end{lstlisting}
    \item Compile and upload the \emph{platformio} project in 
    \begin{lstlisting}
tiny-ml/ugv/codes/client
    \end{lstlisting}
    to the Vaman-ESP32 using USB-UART.
    \item Attach a serial monitor to the terminal with the following command:
    \begin{lstlisting}
pio device monitor -b 115200
    \end{lstlisting}
    \item Start recording in the Sensor Logger app and perform the gestures.
    Verify whether the model works as intended.
    \item Detach the USB-UART from the Vaman-ESP32, and make connections
    to the inputs of the L293 Motor Driver onboard the assembled UGV as per
    \autoref{tab:ugv-connections}.
    \begin{table}[!ht]
        \centering
        \input{tiny-ml/ugv/tables/ugv-connections.tex}
        \caption{Connections Between Vaman-ESP32 and L293 Motor Driver.}
        \label{tab:ugv-connections}
    \end{table} 
\end{enumerate}
