This chapter illustrates a use case of TinyML in gesture detection. A video
demonstration of the experiment described below is present in the 
\href{https://github.com/gadepall/aiml#TinyML}{README} of the repository.

\section{Assets}
\begin{enumerate}
    \item Android phone
    \item USB 2.0/3.0 hub or USB-OTG
    \item LC Vaman board
\end{enumerate}

\section{Training Data}
\begin{enumerate}
    \item Download the Sensor Logger app from Google Play Store.
    \item In the settings on the app, set the sampling frequency up to 100 Hz, 
    and turn off logging uncalibrated data.
    \item Press \texttt{Start Recording}, and perform the gestures 100 times
    to gather the data.
    \item Press \texttt{Stop Recording} when you are done and export the 
    recordings as a zip file.
    \item Unzip and rename the CSV files appropriately in
    \begin{lstlisting}
tiny-ml/data
    \end{lstlisting}
    \item In the same directory, run the following commands:
    \begin{lstlisting}
gcc -O2 format.c
./a.out
    \end{lstlisting}
    \item Two more CSV files \texttt{train.csv} and \texttt{test.csv} will be 
    created in the same directory.
\end{enumerate}

\section{Model}
\begin{enumerate}
    \item Run the Python script
    \begin{lstlisting}
tiny-ml/codes/bin_class.py
    \end{lstlisting}
    \item Tweak the neural network parameters in this file if the accuracy is
    not satisfactory.
    \item The neural network model will be present as a bytestream in
    \begin{lstlisting}
tiny-ml/codes/client/src/gesture_model.h  
    \end{lstlisting}
\end{enumerate}

\section{Implementation}
\begin{enumerate}
    \item Find the IP address of your phone by using the \texttt{ifconfig}
    command.
    \item In the Sensor Logger app, set the HTTP Push URL to
    \begin{lstlisting}
http://<IP>:5000/gesture
    \end{lstlisting}
    in the app settings. Enable the HTTP Push feature.
    \item In \texttt{tiny-ml/codes/server}, run the following command:
    \begin{lstlisting}
flask run --host <IP>
    \end{lstlisting}
    \item In \texttt{tiny-ml/codes/client}, compile and upload the 
    \textit{platformio} project using USB-UART.
    \item Attach a serial monitor to the terminal with the following command:
    \begin{lstlisting}
pio device monitor -b 115200
    \end{lstlisting}
    \item Start recording in the Sensor Logger app and perform the gestures.
    Verify whether the model works as intended.
    \item Implement a decade counter which can increment and decrement the 
    displayed value based on the detected gesture.
\end{enumerate}
